---
title: "Foreign direct investment, net inflows (% of GDP)"
---


**Foreign direct investment** are the net inflows of investment to acquire a lasting management interest (10 percent or more of voting stock) in an enterprise operating in an economy other than that of the investor. It is the sum of equity capital, reinvestment of earnings, other long-term capital, and short-term capital as shown in the balance of payments. This series shows net inflows (new investment inflows less disinvestment) in the reporting economy from foreign investors, and is divided by GDP.

* **ID:** BX.KLT.DINV.WD.GD.ZS
* **Source:** World Bank national accounts data, and OECD National Accounts data files.
* **Periodicity:** Annual
* **Topic:** Economic Policy & Debt: National accounts: US$ at current prices: Aggregate indicators

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(WDI)
dat = WDI(indicator='BX.KLT.DINV.WD.GD.ZS', country='all', start=1960, end=2022)

library(downloadthis)

dat %>%
  download_this(
    output_name = "BX.KLT.DINV.WD.GD.ZS",
    output_extension = ".xlsx",
    button_label = "Download data as xlsx",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-save"
  )

dat %>%
  download_this(
    output_name = "BX.KLT.DINV.WD.GD.ZS",
    output_extension = ".csv",
    button_label = "Download data as csv",
    button_type = "success",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```



<br>
<br>





### Evolution of the indicator from 1960 to 2022



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dat2 = WDI(indicator='BX.KLT.DINV.WD.GD.ZS', country=c('Z4','Z7','ZJ','ZQ','XU','8S','ZG'), start=1960, end=2022)
library(plotly)
plot_ly(dat2, x = ~year, y = ~BX.KLT.DINV.WD.GD.ZS) %>%
  add_lines(linetype = ~country)
```

### Value of the indicator in 2021


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(knitr)
newdata <- dat[ which(dat$year==2021), ]
x=newdata$country
y=newdata$BX.KLT.DINV.WD.GD.ZS
z=as.data.frame(cbind(x,y))
names(z)=c('Country','Value')
knitr::kable(z,digits =2, align = "ll")
```