---
title: "Industry, value added (% of GDP)"
---


**Industry (including construction) corresponds to ISIC divisions 05-43 and includes manufacturing (ISIC divisions 10-33).** It comprises value added in mining, manufacturing (also reported as a separate subgroup), construction, electricity, water, and gas. Value added is the net output of a sector after adding up all outputs and subtracting intermediate inputs. It is calculated without making deductions for depreciation of fabricated assets or depletion and degradation of natural resources. The origin of value added is determined by the International Standard Industrial Classification (ISIC), revision 4. Note: For VAB countries, gross value added at factor cost is used as the denominator.

* **ID:** NV.IND.TOTL.ZS
* **Source:** World Bank national accounts data, and OECD National Accounts data files.
* **Periodicity:** Annual
* **Topic:** Economic Policy & Debt: National accounts: US$ at current prices: Aggregate indicators

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(WDI)
dat = WDI(indicator='NV.IND.TOTL.ZS', country='all', start=1960, end=2022)

library(downloadthis)

dat %>%
  download_this(
    output_name = "NV.IND.TOTL.ZS",
    output_extension = ".xlsx",
    button_label = "Download data as xlsx",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-save"
  )

dat %>%
  download_this(
    output_name = "NV.IND.TOTL.ZS",
    output_extension = ".csv",
    button_label = "Download data as csv",
    button_type = "success",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```



<br>
<br>





### Evolution of the indicator from 1960 to 2022



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dat2 = WDI(indicator='NV.IND.TOTL.ZS', country=c('Z4','Z7','ZJ','ZQ','XU','8S','ZG'), start=1960, end=2022)
library(plotly)
plot_ly(dat2, x = ~year, y = ~NV.IND.TOTL.ZS) %>%
  add_lines(linetype = ~country)
```

### Value of the indicator in 2021


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(knitr)
newdata <- dat[ which(dat$year==2021), ]
x=newdata$country
y=newdata$NV.IND.TOTL.ZS
z=as.data.frame(cbind(x,y))
names(z)=c('Country','Value')
knitr::kable(z,digits =2, align = "ll")
```

