---
title: "GDP growth (annual %)"
---


**Annual percentage growth rate of GDP** at market prices based on constant local currency. Aggregates are based on constant 2015 prices, expressed in U.S. dollars. GDP is the sum of gross value added by all resident producers in the economy plus any product taxes and minus any subsidies not included in the value of the products. It is calculated without making deductions for depreciation of fabricated assets or for depletion and degradation of natural resources.

* **ID:** NY.GDP.MKTP.KD.ZG
* **Source:** Source: World Bank national accounts data, and OECD National Accounts data files.
* **Periodicity:** Annual
* **Topic:** Economic Policy & Debt: National accounts: Growth rates

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(WDI)
dat = WDI(indicator='NY.GDP.MKTP.KD.ZG', country='all', start=1960, end=2022)

library(downloadthis)

dat %>%
  download_this(
    output_name = "NY.GDP.MKTP.KD.ZG",
    output_extension = ".xlsx",
    button_label = "Download data as xlsx",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-save"
  )

dat %>%
  download_this(
    output_name = "NY.GDP.MKTP.KD.ZG",
    output_extension = ".csv",
    button_label = "Download data as csv",
    button_type = "success",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```


<br>
<br>





### Evolution of the indicator from 1960 to 2022



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dat2 = WDI(indicator='NY.GDP.MKTP.KD.ZG', country=c('Z4','Z7','ZJ','ZQ','XU','8S','ZG'), start=1960, end=2022)
library(plotly)
plot_ly(dat2, x = ~year, y = ~NY.GDP.MKTP.KD.ZG) %>%
  add_lines(linetype = ~country)
```

### Value of the indicator in 2021


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(knitr)
newdata <- dat[ which(dat$year==2021), ]
x=newdata$country
y=newdata$NY.GDP.MKTP.KD.ZG
z=as.data.frame(cbind(x,y))
names(z)=c('Country','Value')
knitr::kable(z,digits =2, align = "ll")
```

