---
title: "Unemployment, total (% of total labor force) (modeled ILO estimate)"
---


**Unemployment** refers to the share of the labor force that is without work but available for and seeking employment.



* **ID:** SL.UEM.TOTL.ZS
* **Source:** World Bank national accounts data, and OECD National Accounts data files.
* **Periodicity:** Annual
* **Topic:** Economic Policy & Debt: National accounts: US$ at current prices: Aggregate indicators

```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(WDI)
dat = WDI(indicator='SL.UEM.TOTL.ZS', country='all', start=1960, end=2022)

library(downloadthis)

dat %>%
  download_this(
    output_name = "SL.UEM.TOTL.ZS",
    output_extension = ".xlsx",
    button_label = "Download data as xlsx",
    button_type = "primary",
    has_icon = TRUE,
    icon = "fa fa-save"
  )

dat %>%
  download_this(
    output_name = "SL.UEM.TOTL.ZS",
    output_extension = ".csv",
    button_label = "Download data as csv",
    button_type = "success",
    has_icon = TRUE,
    icon = "fa fa-save"
  )
```



<br>
<br>





### Evolution of the indicator from 1960 to 2022



```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
dat2 = WDI(indicator='SL.UEM.TOTL.ZS', country=c('Z4','Z7','ZJ','ZQ','XU','8S','ZG'), start=1960, end=2022)
library(plotly)
plot_ly(dat2, x = ~year, y = ~SL.UEM.TOTL.ZS) %>%
  add_lines(linetype = ~country)
```

### Value of the indicator in 2021


```{r echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}
library(knitr)
newdata <- dat[ which(dat$year==2021), ]
x=newdata$country
y=newdata$SL.UEM.TOTL.ZS
z=as.data.frame(cbind(x,y))
names(z)=c('Country','Value')
knitr::kable(z,digits =2, align = "ll")
```